```{r, setup, echo = FALSE, message = FALSE, results = "hide"}
knitr::opts_chunk$set(
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
file.copy("../seagull/seagull_0.0.1.tar.gz", ".", overwrite=TRUE)
```

# buildr

A very simple minded build server, until [r-hub](https://github.com/r-hub) is working.  Don't use this for anything serious and use r-hub when it comes out because it's going to be way better.

# Using the client

You need the hostname of the build server, and the port if it is running on a non-deafult port

```{r}
cl <- buildr::buildr_client("localhost", 9999L)
```

Test that the connection is up (I have intermittent connection problems with the server on Windows).

```{r}
cl$ping()
```

(this will hang, possibly forever, if it fails).

**Submit a package**.  The package must be a path to a `tar.gz` file built with `R CMD build` or `devtools::build` (i.e., a *source* package).  The filename will typically have an embedded version number.

```{r}
id <- cl$submit("seagull_0.0.1.tar.gz")
id
```

The identifier is the md5 fingerprint of your source file

You can see source packages that the server knows about:

```{r}
cl$packages()
```

To get the actual name of the source files, pass `translate=TRUE`:

```{r}
cl$packages(translate=TRUE)
```

and request the status of the package you are building:

```{r}
cl$status(id)
```

To block until a package has finished building, use `wait`:

```{r}
filename <- cl$wait(id)
filename
```

The return value here is the filename where the binary has been copied to.  You can also get this with:

```{r}
cl$download(id)
```

(by default, both `wait` and `download` use a temporary directory but this is configurable with the `dest` argument).

The build log can be retrieved:

```{r}
cl$log(id)
```

# Server

The file `inst/run.py` file controlls the server.  Running `./inst/run.py` gives options:

```{r, results="asis", echo=FALSE}
writeLines(c("```", system2(c("inst/run.py", "--help"), stdout=TRUE), "```"))
```
